### 2019-11-25 paper/introduction.tex

$^{233}$U (in the \texttt{Pa-decay tank}) is contaminated with $^{232}$U, which produced from parasitic (n, 2n) reactions on $^{233}$U itself, or on $^{233}$Pa, or on $^{232}$Th. $^{208}$Tl a daughter of $^{232}$U emits intense $\gamma$-radiation and this makes $^{233}$U difficult to handle. Moreover, for nonproliferation reasons, $^{233}$U could be diluted with $^{238}$U which makes it impossible to use for nuclear weapons.

>>>>

$^{233}$U is contaminated with $^{232}$U, which produced from parasitic (n,2n) reactions in $^{233}$Pa, or in $^{232}$Th, or in $^{233}$U itself. $^{208}$Tl a daughter of $^{232}$U emits intense $\gamma$-radiation and this makes $^{233}$U undesirable for nuclear weapons. Moreover, for nonproliferation reasons, bred $^{233}$U could be diluted with $^{238}$U to produce denatured fuel, which not suitable for nuclear weapons \cite{dolan2017molten}.

### 2019-11-25 paper/methods.tex

\begin{table}  %[!ht]
	\caption{The main characteristics of the SD-TMSR \cite{li_optimization_2018}.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{l | r}
		\hline
		Thermal power, MW$_{th}$          				&  2,250  \\ 
		Fuel salt components                            & LiF-BeF$_2$-(\gls{HM})F$_4$ \\
		Fuel composition, mole\%                        & 70-17.5-12.5    \\
		$^7$Li enrichment, \%        				& 99.995   \\
		Fuel temperature, K 							& 900  \\
		Fuel density at 900 K, g/cm$^3$		  		& 3.3 \\
		Fuel dilatation coefficient, g/(cm$^3$$.$K)  &  -6.7$\times$10$^{-4}$ \\
		Graphite density, g/cm$^3$             	    & 2.3	\\  
		B$_4$C density, g/cm$^3$					& 2.52  \\
		$^{10}$B enrichment, \%						&  18.4  \\
		Core diameter, cm								& 460  \\
		Core height, cm									& 460  \\
		Side length of the graphite hexagonal prism, cm   & 7.5 \\
		Inner radius, cm							& 3.5  \\
		Outer radius, cm							& 5  \\
		Ratio of molten salt and graphite in the inner zone	&  0.357  \\
		Ratio of molten salt and graphite in the outer zone &  1.162  \\
		Fuel volume, m$^3$  &	52.9 \\
		\hline
	\end{tabularx}
	\label{tab:table1}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\begin{figure}[t!] % replace 't' with 'b' to \centering
%	\hspace{+0.65in}
%	\includegraphics[width=\textwidth]{core.png}
%	\caption{Plan view of SD-TMSR core.}
%	\label{fig:core}
%\end{figure}

\subsection{Fuel composition}
The general composition of the startup liquid fuel salt in this work is 70LiF - 
17.5BeF$_2$ - 12.5(HM)F$_N$ mole\%, where HM is the heavy metal (mixture of 
thorium and one of these fissile materials: \gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu, \gls{TRU}, and $^{233}$U).
The aim of this paper is to simulate the  
operation of the \gls{SD-TMSR} for 60 years with various startup fissile 
compositions and without any external feed of fissile $^{233}$U which we 
assume is unavailable. For that reason, five different types of initial 
fissile materials are considered based on \gls{HALEU}, Pu, and \gls{TRU} from Light Water
Reactor (LWR) spent nuclear fuel (SNF):
\begin{enumerate}[label=(\alph*)]
	\item High Assay Low Enriched Uranium (HALEU) (19.79\%),
	\item Pu mixed with \gls{HALEU} (19.79\%),
	\item reactor-grade Pu \cite{marka1993explosive},
	\item transuranic (TRU) elements from LWR SNF \cite{de2000scenarios}, and
	\item $^{233}$U for comparison \cite{ashraf2019whole_core}.
\end{enumerate}
All types of initial fissile materials are fed as fluorides.
The reactor-grade Pu and \gls{TRU} compositions are summarized in 
Table~\ref{tab:table2} and ~\ref{tab:table3}, respectively.

\begin{table}  %[!ht]
	\caption{Reactor-grade Pu vector (wt.\%) \cite{marka1993explosive}.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{r r r r r}
		\hline
		$^{238}$Pu & $^{239}$Pu & $^{240}$Pu & $^{241}$Pu & $^{242}$Pu \\
		\hline
		 1.3&60.3&24.3&9.1&5 \\
		\hline
	\end{tabularx}
	\label{tab:table2}
\end{table}

\begin{table}  %[!ht]
	\caption{\gls{TRU} vector (wt.\%) \cite{de2000scenarios}.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{r r r r r r r r r r}
		\hline
		$^{237}$Np&$^{238}$Pu & $^{239}$Pu & $^{240}$Pu & $^{241}$Pu & $^{242}$Pu&$^{241}$Am &$^{243}$Am&$^{244}$Cm &$^{245}$Cm\\
		\hline
		6.3&2.7&45.9&21.5&10.7&6.7&3.4&1.9&0.8&0.1 \\
		\hline
	\end{tabularx}
	\label{tab:table3}
\end{table}

@@

\begin{table}  %[!ht]
	\caption{Initial heavy metal inventories for 
	various initial fissile loadings (kg).}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{X X p{0.18\textwidth} 
	p{0.14\textwidth} X X}
		\hline
		Nuclide & \gls{HALEU} (19.79\%) & Pu+\gls{HALEU} (19.79wt.\%) &  
		reactor-grade Pu & \gls{TRU}& $^{233}$U \\	\hline
		$^{232}$Th       &6.24E+04 & 4.67E+04 &   6.75E+04			& 5.44E+04	& 7.69E+04    \\ 
		$^{233}$U        &         & &        &       &  1.30E+03 \\
		$^{235}$U        & 3.17E+03 &6.01E+03	&            &   & \\
		$^{238}$U      	 &1.28E+04  &2.43E+04 &	&  &\\
		$^{237}$Np	  	 &         && &1.58E+03	&    \\
		$^{238}$Pu	  	 &         &1.60E+01	& 1.13E+02 & 6.78E+02	&   \\
		$^{239}$Pu       &         &9.59E+02&6.76E+03& 1.15E+04&    \\
		$^{240}$Pu       &         &3.99E+02& 2.82E+03&5.40E+03&  	\\  
		$^{241}$Pu		 &         &1.60E+02&1.13E+03&2.69E+03&   \\
		$^{242}$Pu		 &         &6.39E+01	&4.51E+02	& 1.68E+03& \\
		$^{241}$Am		 &         &&& 8.53E+02 & \\
		$^{242}$Am		 &         &&&  &\\
		$^{243}$Am       &        & &&4.77E+02&\\
		$^{244}$Cm		 &        & &&2.01E+02&  \\
		$^{245}$Cm		 &        & &&			2.51E+01	&   \\ 
		\hline
	\end{tabularx}
\label{tab:table5}
\end{table}

@@

As shown in Figure~\ref{fig:flow}, after launching the input file, SERPENT solves the Bateman equation using an advanced 
matrix exponential solution based on the Chebyshev Rational Approximation 
Method \cite{isotalo2016improving}. 
Then, the system extracts gaseous \gls{FPs} and other materials 
(non-dissolved metals, lanthanides, and soluble metals except Pa) with 
a suitable removal rate\footnote{The extraction rate depends on the type of 
poison and its impact on the neutron
economy.}. This is done by setting the 
flow rate of gaseous \gls{FPs} and other materials from the fuel to the 
\texttt{FP-waste tank}\footnote{An external tank used to store the gaseous 
\gls{FPs} and the other materials (non-dissolved metals, lanthanides, and 
soluble metals except protactinium).}. Specifically, Pa is removed 
from the fuel with a certain flow rate into the 
\texttt{Pa-decay tank} to decay and produce $^{233}$U\footnote{The 
$^{233}$Pa is removed and left to decay into $^{233}$U with $\tau_{1/2}$ 
$\approx$ $27$ $d$.}. The produced $^{233}$U is used as a fresh fissile fuel 
and the residual $^{233}$U (if exist) is the net production of $^{233}$U that required to start up a new SD-TMSR and achieve the transition to thorium fuel cycle. The MSR burnup 
routine provided by SERPENT-2 allows changes to the mass flow rates ($mflow$) of the 
isotopes during reactor operation \cite{aufiero2013extended}. Specifically, the SERPENT user should determine the mass flow rate ($mflow$), which is the rate by 
which elements or nuclides are transferred between materials. After that, the 
flow rates must be connected to materials with a reprocessing scheme. 
The final step is to link the reprocessing schemes to depletion histories. In 
the present work, we adjust the transfer rates of fresh fuel to maintain core 
criticality and to keep fuel salt mass constant during burnup. The continuous feed constant calculation procedures are summarized as follows:
\begin{enumerate}
	\item The simulation starts without injecting refueling materials (i.e. only removing FPs and Pa).
	\item After the first depletion calculation step, we check the total mass density of FPs and Pa in the \texttt{FP-waste tank} and \texttt{Pa-decay tank}, respectively.
	\item A simple calculation yields the amount of heavy metal that must be added during this cycle:
	\subitem 3a. \textbf{Thorium feed mechanism}: mass of Th $\approx$ mass of extracted FPs and mass of $^{233}$U $\approx$ mass of extracted Pa.
	\subitem 3b. \textbf{Non-thorium feed mechanism}: mass of external heavy metals (excluding Th) $\approx$ mass of extracted FPs and mass of $^{233}$U $\approx$ mass of extracted Pa.
	\item Dividing this mass by time and inventory of refueling material gives the corresponding feed constant.
\end{enumerate}
The cycle calculation runs iteratively until the burnup reaches the desired worth.

@@

Integration of equation \ref{Equ:1} gives the removal constant $\lambda_{e}$ $[s^{-1}]$ (the rate at which the material 
is removed), where $\lambda_{e}=\dfrac{{\varepsilon_{e}}}{{T}_{r}}$. The removal constant 
$\lambda_{e}$ of gaseous and other fission products is precisely calculated 
and summarized in Table~\ref{tab:table6}. The effective reprocessing time for 
the gaseous \gls{FPs} and non-dissolved metals was set to 30 s (removal 
constant $\lambda_{e}$ = $-0.0333$ $s^{-1}$), because such elements must be 
extracted promptly and continuously via a gas removal system. In contrast, 
chemical processes (i.e. fluorination and reduction) extract the soluble \gls{FPs}, lanthanides, and Pa.
Therefore, the system reprocesses a specific amount of fuel salt daily. In the 
present work, the effective extraction time for soluble \gls{FPs} is 
$\approx$10.59 days ($\lambda_{e}$ = $-1.092\times10^{-6}$ $s^{-1}$), which is 
equivalent to a chemical reprocessing rate of 5 m$^3$/d chosen by Nuttin \emph{et al.} \cite{nuttin2005potential} and Li \emph{et al.} \cite{li_optimization_2018}. The effective feed rates of 
the heavy metals (HM) are changed during reactor operation to conserve the 
total fuel mass and criticality. The effective feed rates for Th/$^{233}$U, reactor-grade Pu, and TRU cases are listed in Table~\ref{tab:table8}, \ref{tab:table9}, and \ref{tab:table10} in \ref{Appendix}.

\begin{table}[ht!]
	\centering
	\caption{The reprocessing table \cite{ashraf2019whole_core}.} 
	\vspace{1ex}
	\begin{tabularx}{\textwidth}{|p{2.3cm}|p{4.5cm}|p{2cm}|p{2cm}|}
			\hline
			\textbf{Reprocessing group}  & \textbf{Element} & \textbf{Reprocessing time} & \textbf{Removal constant} $\lambda_{e}$ $[s^{-1}]$ \\
			\hline
			\raggedright Gaseous \gls{FPs} and non-dissolved metals  &  H, He, N, O, Ne, Ar, Kr, Nb, Mo, Tc, Ru, Rh, Pd, Ag, Sb, Te, Xe, Lu, Hf, Ta, W, Re, Os, Ir, Pt, Au, and Rn.		&	\raggedright 30 s	&  -3.333E-02 \\
			\hline
			\raggedright Lanthanides and other soluble \gls{FPs}     & 
			Zn, Ga, Ge, As, Se, Br, Rb, Sr, Y, Zr, Cd, In, Sn, I, Cs, Ba, La, Ce, Pr, Nd, Pm, Sm, Eu, Gd, Tb, Dy, Ho, Er, Tm, and Yb. & \raggedright 10.59 d (5 m$^3$/d) &  -1.092E-06 \\
			\hline
			Protactinium   & Pa  & \raggedright 10.59 d (5 m$^3$/d)  &  -1.092E-06 \\
			\hline
	\end{tabularx}
	\label{tab:table6}
\end{table}

%\begin{table}[ht!]
%	\centering
%	\caption{The refueling table.} 
%	\vspace{1ex}
%	\begin{tabularx}{\textwidth}{|p{1.5cm}|b|p{1.9cm}|}
%		\hline
%		\textbf{Nuclide} & \textbf{Feed rate} & \textbf{Feed constant$^{\star}$} $\lambda_{e}$ $[s^{-1}]$ \\
%		\hline
%		$^{232}$Th        &  1.842 [Kg/day], first 90 [d] & 1.500E-09 \\
%		&  2.511 [Kg/day], from 90 to 1550 [d] & 		2.045E-09 \\
%		&  2.456 [Kg/day], from 1550 to 3010 [d] & 		2.000E-09 \\
%		&  2.321 [Kg/day], from 3010 to 5930 [d]& 		1.890E-09	\\
%		&  2.241 [Kg/day], from 5930 to 7390 [d] &		1.825E-09	\\
%		&  2.186 [Kg/day], from 7390 to 12500 [d] &		1.780E-09	\\
%		&  2.118 [Kg/day], from 12500 to 15420 [d] &	1.725E-09	\\
%		&  2.136 [Kg/day], from 15420 to 18340 [d]&		1.740E-09		\\
%		&  2.063 [Kg/day], from 18340 to 21900 [d]&		1.680E-09	 \\ 
%		\hline
%		$^{233}$U & 2.619 [Kg/day], first 90 [d]	&   6.400E-09  \\
%		& 2.009 [Kg/day],  form 90 to 1550 [d] &	4.910E-09 \\
%		& 1.944 [Kg/day], from 1550 to 3010 [d] &	4.750E-09 \\
%		& 1.826 [Kg/day],  from 3010 to 5930 [d] &	4.460E-09 \\
%		& 1.811 [Kg/day],  from 5930 to 7390[d] &	4.425E-09 \\
%		& 1.744 [Kg/day], from 7390 to 12500 [d] &	4.260E-09 \\
%		& 1.699 [Kg/day], from 12500 to 18340 [d]	& 4.150E-09 \\
%		& 1.657 [Kg/day], from 18340 to 21900 [d]	& 4.050E-09 \\
%		\hline
%	\end{tabularx}
%	\begin{tablenotes}
%		\small
%		\item  $^{\star}$ Feed constant is the mass fraction of fissile nuclide ($^{232}$Th or $^{233}$U) transferred from the external storage to the core per second.
%	\end{tablenotes}
%	\label{tab:table3}
%\end{table}

>>>>

\begin{table}  %[!ht]
	\caption{The main characteristics of the SD-TMSR \cite{li_optimization_2018}.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{l | r}
		\hline
		Thermal power, MW$_{th}$          				&  2,250  \\ 
		Fuel salt components                            & LiF-BeF$_2$-(\gls{HM})F$_N$ \\
		Fuel composition, mole\%                        & 70-17.5-12.5    \\
		$^7$Li enrichment, \%        				& 99.995   \\
		Fuel temperature, K 							& 900  \\
		Fuel density at 900 K, g/cm$^3$		  		& 3.3 \\
		Fuel dilatation coefficient, g/(cm$^3$$.$K)  &  -6.7$\times$10$^{-4}$ \\
		Graphite density, g/cm$^3$             	    & 2.3	\\  
		B$_4$C density, g/cm$^3$					& 2.52  \\
		$^{10}$B enrichment, \%						&  18.4  \\
		Core diameter, cm								& 460  \\
		Core height, cm									& 460  \\
		Side length of the graphite hexagonal prism, cm   & 7.5 \\
		Inner radius, cm							& 3.5  \\
		Outer radius, cm							& 5  \\
		Ratio of molten salt and graphite in the inner zone	&  0.357  \\
		Ratio of molten salt and graphite in the outer zone &  1.162  \\
		Fuel volume, m$^3$  &	52.9 \\
		\hline
	\end{tabularx}
	\label{tab:table1}
\end{table}

\subsection{Fuel composition}
The general composition of the startup liquid fuel salt in this work is 70LiF - 
17.5BeF$_2$ - 12.5(HM)F$_N$ mole\%, where HM is the heavy metal (mixture of 
thorium and one of these fissile materials: \gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu, \gls{TRU}, and $^{233}$U), and $N$ is dependent on the chosen fissile material and the thermochemical state of the liquid fuel salt.

The aim of this paper is to simulate the  
operation of the \gls{SD-TMSR} for 60 years with various startup fissile 
compositions and without any external feed of fissile $^{233}$U which we 
assume is unavailable. For that reason, five different types of initial 
fissile materials are considered based on \gls{HALEU}, Pu, and \gls{TRU} from Light Water
Reactor (LWR) spent nuclear fuel (SNF):
\begin{enumerate}[label=(\alph*)]
	\item High Assay Low Enriched Uranium (HALEU) (19.79\%),
	\item Pu mixed with \gls{HALEU} (19.79\%),
	\item reactor-grade Pu \cite{marka1993explosive},
	\item transuranic (TRU) elements from LWR SNF \cite{de2000scenarios}, and
	\item $^{233}$U for comparison \cite{ashraf2019whole_core}.
\end{enumerate}
All types of initial fissile materials are fed as fluorides.
The reactor-grade Pu and \gls{TRU} compositions are summarized in 
Table~\ref{tab:table2} and ~\ref{tab:table3}, respectively.

\begin{table} % [!ht]
	\centering
	\caption{Reactor-grade Pu vector (wt.\%) \cite{marka1993explosive}.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{|X |X |X| X| X|}
		\hline
		$^{238}$Pu & $^{239}$Pu & $^{240}$Pu & $^{241}$Pu & $^{242}$Pu \\
		\hline
		 1.3 &60.3&24.3&9.1&5 \\
		\hline
	\end{tabularx}
	\label{tab:table2}
\end{table}

\begin{table} %  [!ht]
	\centering
	\caption{\gls{TRU} vector (wt.\%) \cite{de2000scenarios}.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{|X| X| X| X| X| X| X| X| X| X|}
		\hline
		$^{237}$Np&$^{238}$Pu & $^{239}$Pu & $^{240}$Pu & $^{241}$Pu & $^{242}$Pu&$^{241}$Am &$^{243}$Am&$^{244}$Cm &$^{245}$Cm\\
		\hline
		6.3&2.7&45.9&21.5&10.7&6.7&3.4&1.9&0.8&0.1 \\
		\hline
	\end{tabularx}
	\label{tab:table3}
\end{table}

@@

\begin{table}  %[!ht]
	\caption{Initial heavy metal inventories for 
	various initial fissile loadings (kg).}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{X X p{0.18\textwidth} 
	p{0.14\textwidth} X X}
		\hline
		Nuclide & \gls{HALEU} (19.79 wt.\%) & Pu+\gls{HALEU} (19.79 wt.\%) &  
		reactor-grade Pu & \gls{TRU}& $^{233}$U \\	\hline
		$^{232}$Th       &6.24E+04 & 4.67E+04 &   6.75E+04			& 5.44E+04	& 7.69E+04    \\ 
		$^{233}$U        &         & &        &       &  1.30E+03 \\
		$^{235}$U        & 3.17E+03 &6.01E+03	&            &   & \\
		$^{238}$U      	 &1.28E+04  &2.43E+04 &	&  &\\
		$^{237}$Np	  	 &         && &1.58E+03	&    \\
		$^{238}$Pu	  	 &         &1.60E+01	& 1.13E+02 & 6.78E+02	&   \\
		$^{239}$Pu       &         &9.59E+02&6.76E+03& 1.15E+04&    \\
		$^{240}$Pu       &         &3.99E+02& 2.82E+03&5.40E+03&  	\\  
		$^{241}$Pu		 &         &1.60E+02&1.13E+03&2.69E+03&   \\
		$^{242}$Pu		 &         &6.39E+01	&4.51E+02	& 1.68E+03& \\
		$^{241}$Am		 &         &&& 8.53E+02 & \\
		$^{242}$Am		 &         &&&  &\\
		$^{243}$Am       &        & &&4.77E+02&\\
		$^{244}$Cm		 &        & &&2.01E+02&  \\
		$^{245}$Cm		 &        & &&			2.51E+01	&   \\ 
		\hline
	\end{tabularx}
\label{tab:table5}
\end{table}

@@

As shown in Figure~\ref{fig:flow}, after launching the input file, SERPENT solves the Bateman equation using an advanced 
matrix exponential solution based on the Chebyshev Rational Approximation 
Method \cite{isotalo2016improving}. 
Then, the system extracts gaseous \gls{FPs} and other materials 
(non-dissolved metals, lanthanides, and soluble metals except Pa) with 
a suitable removal rate\footnote{The extraction rate depends on the type of 
poison and its impact on the neutron
economy.}. This is done by setting the 
flow rate of gaseous \gls{FPs} and other materials from the fuel to the 
\texttt{FP-waste tank}\footnote{An external tank used to store the gaseous 
\gls{FPs} and the other materials (non-dissolved metals, lanthanides, and 
soluble metals except protactinium).}. Specifically, Pa is removed 
from the fuel with a certain flow rate into the 
\texttt{Pa-decay tank} to decay and produce $^{233}$U \footnote{The 
$^{233}$Pa is removed and left to decay into $^{233}$U with $\tau_{1/2}$ 
$\approx$ $27$ $d$.}. The produced $^{233}$U is used as a fresh fissile fuel 
and the residual $^{233}$U (if exist) is the net production of $^{233}$U that required to start up a new SD-TMSR and achieve the transition to thorium fuel cycle. The MSR burnup 
routine provided by SERPENT-2 allows changes to the mass flow rates ($mflow$) of the 
isotopes during reactor operation \cite{aufiero2013extended}. Specifically, the SERPENT user should determine the mass flow rate ($mflow$), which is the rate by 
which elements or nuclides are transferred between materials. After that, the 
flow rates must be connected to materials with a reprocessing scheme. 
The final step is to link the reprocessing schemes to depletion histories. In 
the present work, we adjust the transfer rates of fresh fuel to maintain core 
criticality and to keep fuel salt mass constant during burnup. The continuous feed constant calculation procedures are summarized as follows:
\begin{enumerate}
	\item The simulation starts without injecting refueling materials (i.e. only removing FPs and Pa).
	\item After the first depletion calculation step, we check the total mass density of FPs and Pa in the \texttt{FP-waste tank} and \texttt{Pa-decay tank}, respectively.
	\item A simple calculation yields the amount of heavy metal that must be added during this cycle:
	\subitem 3a. \textbf{Thorium feed mechanism}: mass of Th $\approx$ mass of extracted FPs and mass of $^{233}$U $\approx$ mass of extracted Pa.
	\subitem 3b. \textbf{Non-thorium feed mechanism}: mass of external heavy metals (excluding Th) $\approx$ mass of extracted FPs and mass of $^{233}$U $\approx$ mass of extracted Pa.
	\item Dividing this mass by time and inventory of refueling material gives the corresponding feed constant.
\end{enumerate}
The cycle calculation runs iteratively until the burnup reaches the desired worth.

@@

Integration of equation \ref{Equ:1} gives the removal constant $\lambda_{e}$ $[s^{-1}]$ (the rate at which the material 
is removed), where $\lambda_{e}=\dfrac{{\varepsilon_{e}}}{{T}_{r}}$. The removal constant 
$\lambda_{e}$ of gaseous and other fission products is precisely calculated 
and summarized in Table~\ref{tab:table6}. The effective reprocessing time for 
the gaseous \gls{FPs} and non-dissolved metals was set to 30 s (removal 
constant $\lambda_{e}$ = $-0.0333$ $s^{-1}$), because such elements must be 
extracted promptly and continuously via a gas removal system. In contrast, 
chemical processes (i.e. fluorination and reduction) extract the soluble \gls{FPs}, lanthanides, and Pa.
Therefore, the system reprocesses a specific amount of fuel salt daily. In the 
present work, the effective extraction time for soluble \gls{FPs} is 
$\approx$10.59 days ($\lambda_{e}$ = $-1.092\times10^{-6}$ $s^{-1}$), which is 
equivalent to a chemical reprocessing rate of 5 m$^3$/d chosen by Nuttin \emph{et al.} \cite{nuttin2005potential} and Li \emph{et al.} \cite{li_optimization_2018}. The effective feed rates of 
the heavy metals (HM) are changed during reactor operation to conserve the 
total fuel mass and criticality. The effective feed rates for Th/$^{233}$U, reactor-grade Pu, and TRU cases are listed in Table A.1, A.2, and A.3 in \ref{Appendix}.

\begin{table}[ht!]
	\centering
	\caption{The reprocessing table \cite{ashraf2019whole_core}.} 
	\vspace{1ex}
	\begin{tabularx}{\textwidth}{|p{2.3cm}|p{4cm}|p{2.2cm}|p{1.9cm}|}
			\hline
			\textbf{Reprocessing group}  & \textbf{Element} & \textbf{Reprocessing time} & \textbf{Removal constant} $\lambda_{e}$ $[s^{-1}]$ \\
			\hline
			\raggedright Gaseous \gls{FPs} and non-dissolved metals  &  H, He, N, O, Ne, Ar, Kr, Nb, Mo, Tc, Ru, Rh, Pd, Ag, Sb, Te, Xe, Lu, Hf, Ta, W, Re, Os, Ir, Pt, Au, and Rn.		&	\raggedright 30 s	&  -3.333E-02 \\
			\hline
			\raggedright Lanthanides and other soluble \gls{FPs}     & 
			Zn, Ga, Ge, As, Se, Br, Rb, Sr, Y, Zr, Cd, In, Sn, I, Cs, Ba, La, Ce, Pr, Nd, Pm, Sm, Eu, Gd, Tb, Dy, Ho, Er, Tm, and Yb. & \raggedright 10.59 d (5 m$^3$/d) &  -1.092E-06 \\
			\hline
			Protactinium   & Pa  & \raggedright 10.59 d (5 m$^3$/d)  &  -1.092E-06 \\
			\hline
	\end{tabularx}
	\label{tab:table6}
\end{table}
